Molecular transport in human pial perivasculature

### 2024-11-12 paper/supplementary_main.tex
Edit notation
Former-commit-id: 5b20f535011df2fea88ac2135027bc51cd2ba7e4

In terms of domains, interfaces and boundaries, we consider the
parenchyma $\Omega_{\rm PAR} \subset \R^3$ and CSF spaces $\Omega_{\rm
  CSF} \subset \R^3$ with $\Omega = \Omega_{\rm PAR} \cup \Omega_{\rm
  CSF}$. The interface between the parenchyma and CSF spaces is
decomposed

\subsection*{Notation and left-overs}

\paragraph*{To be moved: notation and labels}
The thin pia membrane encloses the brain, and we hence denote the CSF-brain interface with $\Gamma_{\rm pia}$, except for the separately marked surface of the lateral ventricles $\Gamma_{\rm LV}$ (thus $\partial \Omega_{\rm CSF} \bigcap \partial \Omega_{\rm PAR} = \Gamma_{\rm LV} \cup \Gamma_{\rm Pia}$).

We denote the different parts of the outer boundary of $\Omega_{\rm
  CSF}$ with $\Gamma_{\mathrm{skull}}$ facing the dura and skull and
$\Gamma_{\rm SSAS}$ representing the lower interface towards the
spinal subarachnoid space (SSAS). $\Gamma_{\mathrm{skull}}$ is further
subdivided into its lower and upper parts: $\Gamma_{\mathrm{skull^l}}$
and $\Gamma_{\mathrm{skull^u}}$ (compare \Cref{fig:concept}). The
boundary of the spinal cord is denoted by $\Gamma_{\rm{SC}}$, which is
given by $\Gamma_{\rm{SC}} = \partial \Omega_{\rm PAR} \setminus
\partial \Omega_{\rm CSF}$ .

>>>>

In terms of geometrical domains, we consider the parenchyma
$\Omega_{\rm PAR} \subset \R^3$ and CSF spaces $\Omega_{\rm CSF}
\subset \R^3$ with $\Omega = \Omega_{\rm PAR} \cup \Omega_{\rm CSF}$
(see also \Cref{fig:intracranial_domains}). The interface between the
parenchyma and CSF spaces is given by $\partial \Omega_{\rm PAR} \cap
\partial \Omega_{\rm CSF}$ and we separate it as two parts: the
surface of the lateral ventricles $\Gamma_{\rm LV}$ and the remaining
pial interface $\Gamma_{\rm pia}$ (thus $\partial \Omega_{\rm CSF}
\bigcap \partial \Omega_{\rm PAR} = \Gamma_{\rm LV} \cup \Gamma_{\rm
  pia}$). The remaining, outer, boundary of $\Omega_{\rm CSF}$ is
again separated into two parts: $\Gamma_{\rm SSAS}$ represents the
lower interface towards the spinal subarachnoid space (SSAS), while
$\Gamma_{\rm AM}$ is the outer interface towards the arachnoid and
dura membranes. $\Gamma_{\rm AM}$ is further subdivided into its lower
and upper parts: $\Gamma_{\rm AM-L}$ and $\Gamma_{\rm AM-U}$. The
boundary of the spinal cord is denoted by $\Gamma_{\rm{SC}}$ and given
by $\Gamma_{\rm{SC}} = \partial \Omega_{\rm PAR} \setminus \partial
\Omega_{\rm CSF}$ .
